R-LIME\@: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2024-06-30 paper.tex
add anchor explanations
feat: compare coverages between anchor and rlime

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amssymb} % for \mathbb
\usepackage{array} % for m column type
\usepackage{bbm} % for \mathbbm
\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
\usepackage{cleveref} % for \cref
\usepackage{csvsimple} % for \csvreader
\usepackage[T1]{fontenc} % for T1 font encoding
\usepackage{graphicx} % for \includegraphics
\usepackage{pgffor} % for \foreach
\usepackage[labelformat=simple]{subcaption} % for subfigure environment
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

% set the path for figures
\graphicspath{{./src/img}{./src/experiments/exp1}{./src/experiments/exp2}}

@@

\section*{Reviewer Response}
\subsection*{Reviewer \#1}
Suggestions for Rebuttal:
\begin{enumerate}
  \setlength{\itemsep}{15pt}
  \item Offer guidance on how to select optimal parameters for different
        datasets and models.
  \item Include a discussion of other model-agnostic interpretability methods,
        such as SHAP, to provide a more comprehensive overview.

        \vspace{10pt}
        \hspace{.02\textwidth}
        \begin{minipage}{.92\textwidth}%
          Thank you for your suggestion. We added an overview of other
          model-agnostic interpretability methods to the related work section.
        \end{minipage}

  \item Add experimental comparisons with more other model-agnostic \\
        interpretability methods to better evaluate R-LIME's effectiveness.
\end{enumerate}

@@

\subsection*{Reviewer \#5}
\begin{itemize}
  \setlength{\itemsep}{15pt}
  \item It would be beneficial to move the comparison of R-LIME with Anchor
        and LIME to the Related Work section for improved clarity and
        organization.
  \item The authors should consider exploring a more compatible method than the
        KL-LUCB algorithm to achieve higher accuracy. Although the experimental
        results suggest a minor effect, there may be potential underlying issues
        that need to be addressed.
  \item The title of the `Challenges and Future Work' section could be more
        aptly replaced with `Discussion' to better reflect the content.
\end{itemize}

% typeset the header of the contribution
\maketitle

@@

\section{Related Work}
\begin{figure}[tbp]
  \centering
  \def\w{2.5}
  \def\ww{5.0}
  \def\h{0.5}
  \def\hh{1.3}
  \def\hhh{1.8}
  \def\hhhh{2.6}
  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
    \node[nodestyle] (post-hoc) at (0,0){post-hoc};
    \node[nodestyle] (dependent) at (-\w,-\hh){%
      \begin{tabular}{c}
        model-dependent \\
        (DTD~\cite{montavon2017explaining}, LRP~\cite{bach2015pixel})
      \end{tabular}
    };
    \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
    \node[nodestyle] (global) at (0,-\hhhh){%
      \begin{tabular}{c}
        global \\
        (PDP~\cite{friedman2001greedy}, ALE~\cite{apley2020visualizing})
      \end{tabular}
    };
    \node[nodestyle] (local) at (\ww,-\hhhh){%
      \begin{tabular}{c}
        \textbf{local} \\
        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors}, \underline{R-LIME})
      \end{tabular}
    };
    \draw(post-hoc) -- (0,-\h);
    \draw(dependent) -- (-\w,-\h) -- (\w,-\h) -- (agnostic);
    \draw(agnostic) -- (\w,-\hhh);
    \draw(global) -- (0,-\hhh)  -- (\ww,-\hhh) -- (local);
  \end{tikzpicture}
  \caption{%
    Categorization of post-hoc explanation methods.
    We focus on \emph{model-agnostic} and \emph{local} methods,
    which explain model's local behavior using only its output.
  }\label{fig:post-hoc}
\end{figure}
In this section,
we overview existing research on post-hoc explanation methods,
which explain the behavior of black-box models already trained.
As shown in \cref{fig:post-hoc},
post-hoc methods are classified into several categories.

@@

Furthermore, model-agnostic methods are categorized into
\emph{global} and \emph{local} methods based on their locality in input space.
Global methods,
such as partial dependence plots (PDP)~\cite{friedman2001greedy}
and accumulated local effects (ALE)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as local interpretable model-agnostic explanations
(LIME)~\cite{ribeiro2016why} and Anchor~\cite{ribeiro2018anchors},
explain model's behavior in the vicinity of a specific input.
While they offer explanations more simple and accurate
than global methods,
the scope of the explanation is limited locally.

@@

    \def\dir{src/experiments/exp1}
    \def\Asample{0012}
    \def\Bsample{0011}
    \def\index#1{\ifnum#1=0 \Asample\else\Bsample\fi}

    {%
      \def\AB#1{\ifnum#1=0 A\else B\fi}
      \renewcommand{\arraystretch}{1.02}
      \begin{figure}[tbp]
        \foreach\a in {0,1}{%
            \centering
            \begin{subfigure}{\textwidth}
              \centering
              \begin{tabular}{p{14em}m{16em}}
                \toprule
                \csvreader[no head, late after line= \\]{%
                  \dir/\index{\a}.csv
                }{}{%
                \ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii % chktex 1
                }
                \bottomrule
              \end{tabular}
              \caption{Instance~\AB{\a}}
              \vspace{15pt}
            \end{subfigure}
          }
        \vspace{-15pt}
        \caption[Two instances sampled from recidivism dataset]{%
          Two instances sampled from training data of recidivism dataset.
          Each number in parentheses represents the integer value assigned
          to the corresponding categorical value.
        }\label{fig:instance}
      \end{figure}
    }
    {%
      \def\scale{0.315}
      \def\imgwidth{0.495\textwidth}
      \def\hspacebase{\hspace{-1.5em}}
      \def\vspacebase{\vspace{0.5em}}
      \def\vspacebeforecaption{\vspace{-0.4em}}
      \begin{figure}[p]
        \centering
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase{}
          \hspace{1.0em}
          \includegraphics[scale=\scale]{lime-\Asample}
          \vspacebeforecaption{}
          \caption{LIME}\label{fig:A-lime}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase{}
          \hspace{0.5em}
          \includegraphics[scale=\scale]{newlime-\Asample-70}
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.70$)}\label{fig:A-rlime-70}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase{}
          \includegraphics[scale=\scale]{newlime-\Asample-80}
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.80$)}
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase{}
          \hspace{-0.5em}
          \includegraphics[scale=\scale]{newlime-\Asample-90}
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
        \end{subfigure}
        \caption[Explanation for Instance A by LIME and R-LIME]{%
          Explanation for Instance A by LIME and R-LIME\@.
        }\label{fig:A}
      \end{figure}
      \begin{figure}[p]
        \centering
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase{}
          \hspace{-0.7em}
          \includegraphics[scale=\scale]{lime-\Bsample}
          \vspacebeforecaption{}
          \caption{LIME}\label{fig:B-lime}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase{}
          \hspace{0.5em}
          \includegraphics[scale=\scale]{newlime-\Bsample-70}
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.70$)}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase{}
          \hspace{-0.8em}
          \includegraphics[scale=\scale]{newlime-\Bsample-80}
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.80$)}
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase{}
          \hspace{-0.8em}
          \includegraphics[scale=\scale]{newlime-\Bsample-90}
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}\label{fig:B-rlime-90}
        \end{subfigure}
        \caption[Explanation for Instance B by LIME and R-LIME]{%
          Explanation for Instance B by LIME and R-LIME\@.
        }\label{fig:B}
      \end{figure}
    }
  }
\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each feature name represent the contribution
(weight of the linear classifier)
to the output of the black-box classifier,
normalized such that the absolute sum is 1.
The figures display the 5 features with the highest absolute contribution.

Explanations generated by LIME (\cref{fig:A-lime,fig:B-lime}) provide insights
that having a prior offenses (\emph{Priors}),
being served for a long time in prison (\emph{Months-Served}),
and committing a crime against property (\emph{Crime against Property})
primarily contribute to the positive prediction
(prediction that the prisoner will be re-arrested).
On the other hand,
being elderly (\emph{Age}), being married (\emph{Married}),
and being of white race (\emph{Race}) contribute to the negative prediction
(prediction that the prisoner will not be re-arrested).
While these LIME explanations provide valuable insights into the behavior of
the black-box model,
they do not explicitly indicate the application scope of the explanations,
leaving users unable to determine to which prisoners the explanations are applicable.

In contrast, R-LIME expresses the application scope of explanations
as a conjunction of feature predicates.
For example, the explanation for instance A
under $\tau=0.70$ (\cref{fig:A-rlime-70}) indicates that it is applicable
only to married prisoner (\emph{Married} $=$\emph{Yes}).
R-LIME explanations also provide their accuracy and coverage,
allowing users to evaluate reliability and generality of the explanations.
For example, the coverage of the explanation for instance B under $\tau=0.90$
(\cref{fig:B-rlime-90}) is 0.01\%,
indicating that the decision boundaries around instance B are complex,
making it challenging to obtain a high-accuracy linear approximation.
This information allows users to discern that
the application scope of this explanation is very narrow, limiting its utility.

\subsection{Quantitative Evaluation}
\subsubsection{Experimental Setup}
To demonstrate that R-LIME learns a highly accurate linear approximation model
in the optimized approximation region,
we conducted a comparison of the local accuracy of explanations
between LIME and R-LIME\@.
Under the same settings as in \cref{sec:exp-setting},
we randomly sampled 100 instances from the test data of the recidivism dataset
and generated explanations using LIME and R-LIME (with $\tau=0.70,0.80,0.90$).
We then sampled 10,000 instances within the rectangular region
obtained by R-LIME and calculated the local accuracy of both methods.
\subsubsection{Experimental Results}
\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.5\textwidth]{box_plot}
  \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
    Comparison of local accuracy between LIME and R-LIME\@.
    R-LIME achieved higher and less variable accuracy compared to LIME
    for all values of $\tau$.
  }\label{fig:box-plot}
\end{figure}
The results are presented in \cref{fig:box-plot},
showing the distribution of the local accuracy of the linear classifiers
learned by LIME and R-LIME\@.
R-LIME achieved higher accuracy compared to LIME for all values of $\tau$.
This suggests that the linear classifiers learned by LIME and R-LIME
differ significantly,
and R-LIME learns a high-accuracy linear classifier
adapted to the optimized rectangular region.
Additionally, as $\tau$ increases,
the variability in the accuracy of LIME widens.
This indicates that the linear classifiers learned by LIME may not function
effectively as approximation models depending on how the region is selected.

\section{Challenges and Future Work}
 {%
  \def\imgwidth{0.47\textwidth}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime3}
      \caption{R-LIME for balanced label distribution.}
    \end{subfigure}
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
      \caption{R-LIME for imbalanced label distribution.
      }
    \end{subfigure}
    \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
      Behavior of R-LIME for balanced and imbalanced label distribution.
      In case of imbalanced label distribution,
      the approximation region covers the entire input space and the
      linear approximation model always outputs the majority label.
    }\label{fig:imbalanced}
  \end{figure}
 }

>>>>

\usepackage[export]{adjustbox} % for valign option in \includegraphics
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amssymb} % for \mathbb
\usepackage{array} % for m column type
\usepackage{bbm} % for \mathbbm
\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
\usepackage{cleveref} % for \cref
\usepackage{color,soul} % for \hl
\usepackage{csvsimple} % for \csvreader
\usepackage[T1]{fontenc} % for T1 font encoding
\usepackage{graphicx} % for \includegraphics
\usepackage{pgffor} % for \foreach
\usepackage[labelformat=simple]{subcaption} % for subfigure environment
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

% set the path for figures
\graphicspath{{./src/img}{./src/experiments}}

@@

{%
  \newenvironment{mycomment}{
    \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
      }{\end{minipage}}
  \section*{Reviewer Response}
  We would like to appriciate all the reviewers for their very helpful comments.
  We added an overview of other existing methods, discussion about parameter
  selection, and comparisons between Anchor and R-LIME\@.
  Below are suggestions from reviewers and our response.

  \subsection*{Reviewer \#1}
  Suggestions for Rebuttal:
  \begin{enumerate}
    \setlength{\itemsep}{15pt}
    \item Offer guidance on how to select optimal parameters for different
          datasets and models.

          \begin{mycomment}
            Thank you for your suggestion. We added guidance on how parameters
            should be selected in practical use cases to \cref{sec:discussion}.
          \end{mycomment}

    \item Include a discussion of other model-agnostic interpretability methods,
          such as SHAP, to provide a more comprehensive overview.

          \begin{mycomment}
            Thank you for your suggestion. We added an overview of other
            model-agnostic interpretability methods to \cref{sec:related-work}.
          \end{mycomment}

    \item Add experimental comparisons with more other model-agnostic \\
          interpretability methods to better evaluate R-LIME's effectiveness.

          \begin{mycomment}
            Thank you for your suggestion. We additionally conducted qualitative
            and quantitative comparisons between Anchor and R-LIME,
            which demonstrated that R-LIME is more effective than Anchor.
          \end{mycomment}
  \end{enumerate}

@@

  \begin{mycomment}
    Thank you for your insightful comments.
  \end{mycomment}

  \subsection*{Reviewer \#5}
  \begin{itemize}
    \setlength{\itemsep}{15pt}
    \item It would be beneficial to move the comparison of R-LIME with Anchor
          and LIME to the Related Work section for improved clarity and
          organization.

          \begin{mycomment}
            Thank you for your suggestion.

            \ldots
          \end{mycomment}

    \item The authors should consider exploring a more compatible method than the
          KL-LUCB algorithm to achieve higher accuracy. Although the experimental
          results suggest a minor effect, there may be potential underlying issues
          that need to be addressed.

          \begin{mycomment}
            Thank you for your valuable feedback.
            It is true that there are theoretical issues for using the KL-LUCB
            algorithm, although our results suggest that its practical effect
            is negligible.
            We leave the issues to the future work because of our limited time.
          \end{mycomment}

    \item The title of the `Challenges and Future Work' section could be more
          aptly replaced with `Discussion' to better reflect the content.

          \begin{mycomment}
            Thank you for your suggestion. We renamed the section to `Discussion'.
          \end{mycomment}
  \end{itemize}
}

% Reset page number and typeset title
\newpage
\setcounter{page}{1}
\maketitle

@@

\section{Related Work}\label{sec:related-work}
\begin{figure}[tbp]
  \centering
  \def\w{2.5}
  \def\ww{5.0}
  \def\h{0.5}
  \def\hh{1.3}
  \def\hhh{1.8}
  \def\hhhh{2.6}
  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
    \node[nodestyle] (post-hoc) at (0,0){post-hoc};
    \node[nodestyle] (dependent) at (-\w,-\hh){%
      \begin{tabular}{c}
        model-dependent \\
        (DTD~\cite{montavon2017explaining}, LRP~\cite{bach2015pixel})
      \end{tabular}
    };
    \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
    \node[nodestyle] (global) at (0,-\hhhh){%
      \begin{tabular}{c}
        global \\
        (PDP~\cite{friedman2001greedy}, ALE~\cite{apley2020visualizing})
      \end{tabular}
    };
    \node[nodestyle] (local) at (\ww,-\hhhh){%
      \begin{tabular}{c}
        \textbf{local} \\
        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors}, \underline{R-LIME})
      \end{tabular}
    };
    \draw(post-hoc) -- (0,-\h);
    \draw(dependent) -- (-\w,-\h) -- (\w,-\h) -- (agnostic);
    \draw(agnostic) -- (\w,-\hhh);
    \draw(global) -- (0,-\hhh)  -- (\ww,-\hhh) -- (local);
  \end{tikzpicture}
  \caption{%
    Categorization of post-hoc explanation methods.
    We focus on \emph{model-agnostic} and \emph{local} methods,
    which explain model's local behavior using only its output.
  }\label{fig:post-hoc}
\end{figure}
In this section,
we overview existing research on post-hoc explanation methods,
which explain the behavior of black-box models already trained.
As shown in \cref{fig:post-hoc},
post-hoc methods are classified into several categories.

@@

Furthermore, model-agnostic methods are categorized into
\emph{global} and \emph{local} methods based on their locality in input space.
Global methods,
such as partial dependence plots (PDP)~\cite{friedman2001greedy}
and accumulated local effects (ALE)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as local interpretable model-agnostic explanations
(LIME)~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors} and
\hl{shapley additive explanations (SHAP)}~\cite{lundberg2017unified},
explain model's behavior in the vicinity of a specific input.
While they offer explanations more simple and accurate
than global methods,
the scope of the explanation is limited locally.

@@

    \def\dir{src/experiments/exp1/ver1/examples/output}
    \def\Asample{0012}
    \def\Bsample{0011}
    \def\index#1{\ifnum#1=0 \Asample\else\Bsample\fi}

    {%
      \def\AB#1{\ifnum#1=0 A\else B\fi}
      \renewcommand{\arraystretch}{1.02}
      \begin{figure}[tbp]
        \foreach\a in {0,1}{%
            \centering
            \begin{subfigure}{\textwidth}
              \centering
              \begin{tabular}{p{14em}m{16em}}
                \toprule
                \csvreader[no head, late after line= \\]{%
                  \dir/\index{\a}.csv
                }{}{%
                \ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii % chktex 1
                }
                \bottomrule
              \end{tabular}
              \caption{Instance~\AB{\a}}
              \vspace{15pt}
            \end{subfigure}
          }
        \vspace{-15pt}
        \caption[Two instances sampled from recidivism dataset]{%
          Two instances sampled from training data of recidivism dataset.
          Each number in parentheses represents the integer value assigned
          to the corresponding categorical value.
        }\label{fig:instance}
      \end{figure}
    }
    {%
      \def\scale{0.315}
      \def\dir{exp1/ver1/examples/output}
      \def\imgwidth{0.3\textwidth}
      \def\hspacebase{\hspace{-1.5em}}
      \def\vspacebase{\vspace{0.5em}}
      \def\vspacebeforecaption{\vspace{-0.4em}}

      \newcommand{\limesubfigure}[2]{
        \begin{subfigure}[t]{\textwidth}
          \hspace{#2}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-\index{#1}}
          \caption{LIME}\label{fig:lime-#1}
          \vspace{1.0em}
        \end{subfigure}
      }
      \newcommand{\anchorsubfigure}[1]{
        \foreach{\a} in {70,80,90}{
            \begin{subfigure}[t]{\textwidth}
              \centering
              \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-\index{#1}-\a}
              \caption{\hl{Anchor ($\tau=0.\a$)}}
              \vspace{1.0em}
            \end{subfigure}
          }
      }
      \newcommand{\rlimesubfigure}[3]{
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{#3}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-\index{#1}-#2}
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.#2$)}\label{fig:rlime-#1-#2}
          \vspacebase{}
        \end{subfigure}
      }
      \begin{figure}[t]
        \begin{subfigure}[t]{0.45\textwidth}
          \centering
          \limesubfigure{0}{-10pt}
          \anchorsubfigure{0}
        \end{subfigure}
        \hfill
        \begin{subfigure}[t]{0.45\textwidth}
          \rlimesubfigure{0}{70}{-10pt}

          \vspace{12pt}
          \rlimesubfigure{0}{90}{-22pt}
        \end{subfigure}
        \caption[Explanation for Instance A by LIME and R-LIME]{%
          Explanation for Instance A by LIME and R-LIME\@.
        }\label{fig:A}
      \end{figure}
      \begin{figure}[t]
        \begin{subfigure}[t]{0.45\textwidth}
          \limesubfigure{1}{-30pt}
          \anchorsubfigure{1}
        \end{subfigure}
        \hfill
        \begin{subfigure}[t]{0.45\textwidth}
          \rlimesubfigure{1}{70}{-10pt}

          \vspace{18pt}
          \rlimesubfigure{1}{90}{-25pt}
        \end{subfigure}
        \caption[Explanation for Instance B by LIME and R-LIME]{%
          Explanation for Instance B by LIME and R-LIME\@.
        }\label{fig:B}
      \end{figure}
    }
  }
\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each feature name represent the contribution
(weight of the linear classifier)
to the output of the black-box classifier,
normalized such that the absolute sum is 1.
The figures display the 5 features with the highest absolute contribution.

Explanations generated by LIME (\cref{fig:lime-0,fig:lime-1}) provide insights
that having a prior offenses (\emph{Priors}),
being served for a long time in prison (\emph{Months-Served}),
and committing a crime against property (\emph{Crime against Property})
primarily contribute to the positive prediction
(prediction that the prisoner will be re-arrested).
On the other hand,
being elderly (\emph{Age}), being married (\emph{Married}),
and being of white race (\emph{Race}) contribute to the negative prediction
(prediction that the prisoner will not be re-arrested).
While these LIME explanations provide valuable insights into the behavior of
the black-box model,
they do not explicitly indicate the application scope of the explanations,
leaving users unable to determine to which prisoners the explanations are applicable.

In contrast, R-LIME expresses the application scope of explanations
as a conjunction of feature predicates.
For example, the explanation for instance A
under $\tau=0.70$ (\cref{fig:rlime-0-70}) indicates that it is applicable
only to married prisoner (\emph{Married} $=$\emph{Yes}).
R-LIME explanations also provide their accuracy and coverage,
allowing users to evaluate reliability and generality of the explanations.
For example, the coverage of the explanation for instance B under $\tau=0.90$
(\cref{fig:rlime-1-90}) is 0.01\%,
indicating that the decision boundaries around instance B are complex,
making it challenging to obtain a high-accuracy linear approximation.
This information allows users to discern that
the application scope of this explanation is very narrow, limiting its utility.

\begin{figure}[t]
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.36,valign=t]{exp2/box_plot}
    \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
      Comparison of local accuracy between LIME and R-LIME\@.
      R-LIME achieved higher and less variable accuracy compared to LIME\@.
    }\label{fig:box-plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.35,valign=t]{exp2b/comp_cov}
    \vspace{3pt}
    \caption[Comparison of Coverage between Anchor and R-LIME]{%
      \hl{%
        Comparison of coverage between Anchor and R-LIME\@.
        R-LIME achieved higher coverage compared to Anchor
        for almost values of $\tau$, especially for relatively small $\tau$.
      }
    }\label{fig:coverage}
  \end{subfigure}
  \caption{Comparison of existing methods (LIME, Anchor) and R-LIME.}
\end{figure}

\subsection{Quantitative Evaluation: LIME vs. R-LIME}

\subsubsection{Experimental Setup}
To demonstrate that R-LIME learns a highly accurate linear approximation model
in the optimized approximation region,
we conducted a comparison of the local accuracy of explanations
between LIME and R-LIME\@.
Under the same settings as in \cref{sec:exp-setting},
we randomly sampled 100 instances from the test data of the recidivism dataset
and generated explanations using LIME and R-LIME (with $\tau=0.70,0.80,0.90$).
We then sampled 10,000 instances within the rectangular region
obtained by R-LIME and calculated the local accuracy of both methods.

\subsubsection{Experimental Results}
The results are presented in \cref{fig:box-plot},
showing the distribution of the local accuracy of the linear classifiers
learned by LIME and R-LIME\@.
R-LIME achieved higher accuracy compared to LIME for all values of $\tau$.
This suggests that the linear classifiers learned by LIME and R-LIME
differ significantly,
and R-LIME learns a high-accuracy linear classifier
adapted to the optimized rectangular region.
Additionally, as $\tau$ increases,
the variability in the accuracy of LIME widens.
This indicates that the linear classifiers learned by LIME may not function
effectively as approximation models depending on how the region is selected.

\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}
\subsubsection{\hl{Experimental Setup}}
\hl{
  To demonstrate that R-LIME explanations are more general than Anchor,
  we conducted a comparison of the coverage of explanations
  between Anchor and R-LIME\@.
  Under the same settings as in
}\cref{sec:exp-setting},
\hl{
  we generated Anchor and R-LIME explanations
  for 100 instances from the test data of the recidivism dataset,
  under the values of $\tau=0.70,0.80,0.90$.
}

\subsubsection{\hl{Experimental Results}}
\hl{The results are presented in} \cref{fig:coverage},
\hl{
  showing the coverage of the explanations by Anchor and R-LIME\@.
  The coverage of explanations generated by R-LIME is higher compared to Anchor
  for almost values of $\tau$, especially for relatively small $\tau$.
  It is because of the flexibility of the linear approximation models learned by
  R-LIME, which captures the decision boundary more precisely.
  In contrast,
  Anchor uses only the intervals of each feature discretized in advance,
  which cannot capture the decision boundary flexibly and makes its scope narrow.
}

\section{\hl{Discussion}}\label{sec:discussion}
{%
  \def\imgwidth{0.47\textwidth}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime3}
      \caption{R-LIME for balanced label distribution.}
    \end{subfigure}
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
      \caption{R-LIME for imbalanced label distribution.
      }
    \end{subfigure}
    \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
      Behavior of R-LIME for balanced and imbalanced label distribution.
      In case of imbalanced label distribution,
      the approximation region covers the entire input space and the
      linear approximation model always outputs the majority label.
    }\label{fig:imbalanced}
  \end{figure}
}
